---
title: "Homework#4"
author: "Jianwen Wu"
date: "5/2/2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

## Problem 7

### In this problem, you will use support vector approaches in order to predict whether a given car gets high or low gas mileage based on the Auto data set.

```{r, message=FALSE}
library(tidyverse)
library(ISLR)
library(e1071)
data("Auto")
```


### part a.

Create a binary variable that takes on a 1 for cars with gas mileage above the median, and a 0 for cars with gas mileage below the median.

```{r}
gas_med = median(Auto$mpg)
Auto <- Auto %>%
  mutate(mpg_level = ifelse(mpg > gas_med, 1, 0))
Auto$mpg_level <- as.factor(Auto$mpg_level)
```


### Part b

Fit a support vector classifier to the data with various values of cost, in order to predict whether a car gets high or low gas mileage. Report the cross-validation errors associated with dif- ferent values of this parameter. Comment on your results.

```{r}
tune_SVM_linear <- tune(svm, mpg_level ~ ., data = Auto, kernel = "linear", ranges = list(cost = c(0.01, 0.1, 1, 5, 10, 100, 1000)))
summary(tune_SVM_linear)
tune_SVM_linear$best.parameters
tune_SVM_linear$best.performance
```

Based on the result, cost at 1 performed the best with cross validation error 0.01025641.


### Part c.

Now repeat (b), this time using SVMs with radial and polynomial basis kernels, with different values of gamma and degree and cost. Comment on your results.

#### Polynomial
```{r}
tune_SVM_poly = tune(svm, mpg_level ~ ., data = Auto, kernel = "polynomial", ranges = list(cost = c(0.1, 
    1, 5, 10), degree = c(2, 3, 4, 5)))
summary(tune_SVM_poly)
tune_SVM_poly$best.parameters
tune_SVM_poly$best.performance
```

Based on the result, cost at 10 and degree at 2 performed the best with cross validation error 0.5380769

#### Radial

```{r}
tune_SVM_radial = tune(svm, mpg_level ~ ., data = Auto, kernel = "radial", ranges = list(cost = c(0.1, 
    1, 5, 10), gamma = c(0.01, 0.1, 1, 5, 10, 100)))
summary(tune_SVM_radial)
tune_SVM_radial$best.parameters
tune_SVM_radial$best.performance
```

Based on the result, cost at 10 and gamma at 0.01 performed the best with cross validation error 0.02564103.


### Part d.

Make some plots to back up your assertions in (b) and (c).

```{r}
SVM_linear <- svm(mpg_level ~ ., data = Auto, kernel = "linear", cost = 1)
SVM_poly <- svm(mpg_level ~ ., data = Auto, kernel = "polynomial", cost = 10, degree = 2)
SVM_radial <- svm(mpg_level ~ ., data = Auto, kernel = "radial", cost = 10, gamma = 0.01)
plotpairs = function(fit) {
    for (name in names(Auto)[!(names(Auto) %in% c("mpg", "mpg_level", "name"))]) {
        plot(fit, Auto, as.formula(paste("mpg~", name, sep = "")))
    }
}
```

#### Linear SVM Plot
```{r}
plotpairs(SVM_linear)
```

#### Ploy SVM Plot

```{r}
plotpairs(SVM_poly)


```

### Radical SVM Plot
```{r}
plotpairs(SVM_radial)

```
