---
title: "Homework#5_ML"
author: "jianwen wu"
date: "5/10/2018"
output:
  pdf_document: default
  html_document: default
---

## Problem 9. 

Consider the USArrests data. We will now perform hierarchical clus- tering on the states.

```{r}
library(tidyverse)
library(ISLR)
data(USArrests)
```


### Part a.

Using hierarchical clustering with complete linkage and Euclidean distance, cluster the states

```{r}
HC_complete <- hclust(dist(USArrests), method = "complete")
plot(HC_complete)
```


### Part b.

Cut the dendrogram at a height that results in three distinct clusters. Which states belong to which clusters?

```{r}
cutree(HC_complete, 3)
table(cutree(HC_complete, 3))
```




### Part c.

Hierarchically cluster the states using complete linkage and Eu- clidean distance, after scaling the variables to have standard de- viation one.

```{r}
scale_data = scale(USArrests)
HC_S_complete = hclust(dist(scale_data), method="complete")
plot(HC_S_complete)
```


### Part d.

What effect does scaling the variables have on the hierarchical clustering obtained? In your opinion, should the variables be scaled before the inter-observation dissimilarities are computed? Provide a justification for your answer.

```{r}
cutree(HC_S_complete, 3)
table(cutree(HC_S_complete, 3))
table(cutree(HC_S_complete, 3), cutree(HC_complete, 3))
```

Scalling the variables affects the max height of the dendogram obtained from the hierachical clustering.  I think the variables should be scaled, because data measures have different unit. For example, X1 has range from 100 to 1000 and X2 has range from 1 to 20.
